Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-28 chapters/introduction/introduction.tex
before fine location and orientation section

We make contributions in three main areas: 1) we proposed a general
probabilistic model to jointly estimate the geo-calibration
parameters, 2) we decomposed the full geo-calibration into several
partial geo-calibration tasks, each of which provides a strong
constraint function that fits into the general model, and 3) we show
that learning to geo-calibrate a camera is helpful for high-level
image feature extraction.

The first two contributions form our main approach. Our
algorithm feeds inputs (images, time and manual annotations) to
different constraint models, which work as constraint functions. Then
we fuse these constraint functions to simulate the joint distribution
over the complete geo-calibration parameters. We present the flowchart of
our approach in \figref{intro:architecture}.

Furthermore, we also explore to learning high-level visual features
and geo-calibrating cameras simultaneously.  We believe that camera
poses, geographic locations and image capture times are closely
related to image representations. 
Imagine a human geo-localizing a camera from an image it took, one
could roughly guess where a photo was taken when she sees an polar
bear on an iceberg. In this scenario, learning high-level
features becomes a necessary process of abstracting visual hints to
localize the camera.
Based on this belief, we designed neural networks to learn useful
visual features by solving geo-calibration tasks. Our work provide new
ways for automatic feature learning.

\subsection{General Probabilistic Model for Geo-Calibration}
We design a general model to estimate the probability over all
geo-calibration parameters. First, we model the process of projecting
from the scene at given location, time, and in given camera pose.
%This the appearance of the image frame are determined by the pin-hole
%model and the geographic location of the camera.
We use a scoring function to measure the ``fitness'' between these
geo-calibration parameters and the appearance of the image. 
The scoring function is proportional to the probability distribution
over the geo-calibration parameters, but the denominator is unknown. We
then propose a Markov Chain Monte Carlo (MCMC) sampling approach to
approximate the underlying probability distribution.
Our model is a general architecture, which can take different
constraints to form the scoring function. The details of this model
can be found in \chapref{mcmc}.

\subsection{Developing Constraint Functions}
In the general model, we define the scoring function is as a weighted
summation of a series of constraint functions.
In the rest of the work, we focus on developing good constraint
functions for different set of geo-calibration parameters. 
A constraint function outputs a score or probability for some given
geo-calibration parameters conditional on the input image.

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Camera Pose:}
  In this constraint we model the camera roll and pitch angles.
  Assuming the intrinsic parameters are known, camera roll and pitch
  angles can be derived from the horizon line position on the image.
  Compared to directly detecting the camera pose, identifying horizon
  line is easier because it is tightly related to the scene layout.
  In our work, we create a new method using CNN to estimate the
  prior distribution over the horizon line. We assign a probability to
  each horizon candidate sampled from the prior distribution by
  measuring their consistences with vanishing points detected using
  traditional statistic methods. We present the algorithm details in
  \chapref{fasthorizon}.  \newline

  \item \textbf{Constraint for Time and Coarse Location:}
  In this work, we demonstrate to estimate probability over the
  capture time and the camera geographic location given the input image.
  Our network has two branches which predict the image
  capture time and the geographic location simultaneously.
  For time estimation, our network is able to predict the
  joint distribution over the month of the year and the UTC hour of the
  day when the input image has been captured.
  For coarse camera geo-localization, We provide two approaches to
  obtain the probability distribution over the camera geographic
  location. Most straightforwardly, our network outputs the discrete
  distribution over the location in the world, which is uniformly
  divided as a 2D meshgrid. Better results can be procured with the
  image capture time as auxiliary input (if it is known). 
  We present the algorithm details in \chapref{whenwhere}.
  \newline

>>>>

We make contributions in three main areas: 1) we proposed a general
probabilistic model to jointly estimate the geo-calibration
parameters, 2) we decomposed the full geo-calibration into several
partial geo-calibration tasks, each of which provides a strong
constraint function that fits into the general model, and 3) we show
that learning to geo-calibrate a camera is a useful pretext for image
feature learning.

The first two contributions make our main approach. Our
algorithm feeds inputs (images, time and manual annotations) to
different constraint functions. Then
we fuse these constraint functions to simulate the joint distribution
over the complete geo-calibration parameters. We present the flowchart of
our approach in \figref{intro:architecture}.

Furthermore, we also explore to learning image features
and geo-calibrating cameras simultaneously.  We believe that camera
poses, geographic locations and image capture times are closely
related to image representations. 
Based on the belief that visual features which abstract the image
contents are the necessary for solving the geo-calibration tasks, we
designed neural networks to learn useful visual features by
geo-calibrating cameras. Our work provide new ways for automatic
feature learning.

\subsection{General Probabilistic Model for Geo-Calibration}
We design a general model to estimate the probability over all
geo-calibration parameters. First, we model the process of projecting
from the scene at given location, time, and in given camera pose.
%This the appearance of the image frame are determined by the pin-hole
%model and the geographic location of the camera.
We use a scoring function to measure the ``fitness'' between these
geo-calibration parameters and the appearance of the image. 
The scoring function is proportional to the probability distribution
over the geo-calibration parameters, but the denominator is unknown. We
then propose a Markov Chain Monte Carlo (MCMC) sampling approach to
approximate the underlying probability distribution.
Our model is flexible that it is able to contribute different
constraint functions to the scoring function. The details of this model
can be found in \chapref{mcmc}.

\subsection{Developing Constraint Functions}
In the general model, we define the scoring function as a weighted
summation of a series of constraint functions.
In the rest of the work, we focus on developing good constraint
functions for different sets of geo-calibration parameters. 
A constraint function outputs a score or probability for some given
geo-calibration parameters conditional on the input image.

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Camera Pose:}
  In this constraint, we model the camera roll and pitch angles.
  Assuming the intrinsic parameters are known, camera roll and pitch
  angles can be derived from the horizon line position on the image.
  Compared to directly detecting the camera pose, identifying horizon
  line is easier because it is reflected by the scene layout.
  In our work, we create a new method using CNN to estimate the
  prior distribution over the horizon line. We assign a probability to
  each horizon candidate sampled from the prior distribution by
  measuring their consistences with detected vanishing points. We
  present the algorithm details in \chapref{fasthorizon}.  \newline

  \item \textbf{Constraint for Time and Coarse Location:}
  In this work, we estimate the probability over the
  capture time and the camera geographic location given the input image.
  Our network has two branches which predict the image
  capture time and the geographic location simultaneously.
  For time estimation, our network is able to predict the
  joint distribution over the month of the year and the UTC hour of the
  day when the input image has been captured.
  For coarse camera geo-localization, We provide two approaches to
  obtain the probability distribution over the camera geographic
  location. Most straightforwardly, our network outputs the discrete
  distribution over the geographic location of the camera. Better
  results can be procured with the image capture time as auxiliary input
  (if it is known).  We present the algorithm details in
  \chapref{whenwhere}.
  \newline
